### 2016-09-30 notions.tex
cheers

Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
\jnote{Here it would not be hard to write the definition for general data structures, not
specifically set-multiplicity data structures.}
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
%\footnote{We do not give $A$ an oracle for issuing queries;
%since $A$ knows the set~$S$, such an oracle would be superfluous.
%\jnote{Interestingly,
%if we provided a query oracle in the real world and an oracle that returns the correct
%answer in the simulated world, then the definition seems to imply
%correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\setprim}{A}=1} -
\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
if for all efficient $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{The definition
as stated does not really work well in the presence of (programmable) random oracles.}
\jnote{In the current definition there is (intentionally) no bound on the simulator's
running time.}
\todo{Mention why giving a Test oracle to A doesn't seem to help.}
\begin{figure}[tp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\setprim}{A}$}\\
$S \getsr A$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}}{A, \Sim}$}\\
$S \getsr A$\\
$\pubaux \getsr \Sim({\sf leak}(S))$ \\
return $A(\pubaux)$\\
}
}
\caption{Experiments for the ``semantic-security'' privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

%\begin{figure}[hbtp]
%\centering
%\fpage{.6}{
%\hpagess{.5}{.45}
%{
%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$ \\
%$(\pubaux,\privaux) \getsr \Rep(S)$\\
%return $A(S,\pubaux)$\\
%}
%%
%{
%\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}, \distr{}{}}{A, \Sim}$}\\
%$S \getsr \distr{}{}$\\
%$\pubaux \getsr \Sim({\sf leak}(S))$ \\
%return $A(S,\pubaux)$\\
%}
%}
%\caption{Experiments for the ``distibutional semantic-security'' privacy
%  definition.}
%\label{fig:privacy-dss}
%\end{figure}
\todo{A simple theorem that says if $\privaux=\emptystring$ then
  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
It's at least worth a highlighted remark, I think.  Currently it is a
remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
\todo{Since we mention what happens with $\privaux=\emptystring$, also
mention what happens with $\pubaux=\emptystring$ :)}
\heading{Relationships between the notions.}
Intuition suggests that semantic security should imply one-wayness. And, indeed, this is
the case---provided one is careful with the technical details.
For a distribution ${\cal D}$
over subsets of some universe ${\cal X}$, define
\[\tilde H_\infty({\cal D} \mid {\sf leak}) \bydef -\log \sum_{r \in R} \Pr_{S \getsr {\cal D}}[{\sf leak}(S)=r] \cdot
\max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r].\]

\jnote{Make theorem statements consistent -- get rid of $(t, \epsilon)$-style.}

@@

\heading{Privacy of ``canonical'' data structures. }
Here we prove a result that can be used to show that a large class of canonical
data structures are SS-secure, with respect to leakage of the size of the set.
\jnote{It would not be too hard to generalize this to arbitrary data structures over
arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
depends only on ${\sf leak}$.}
We first define what we mean by ``canonical.''

@@

\begin{definition}
A data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows:
(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$.
%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$.
\end{itemize}
We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
  this canonical representation handles $\privaux$, too.} \jnote{It
  doesn't matter what priv is.}
\end{definition}
%\jnote{Not sure how general to make the above. Need to verify that it is general enough
%to prove security of all the constructions we care about.}
\tsnote{Point out an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. (Although the following theorem does
  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
  \jnote{I say we state the general theorem in Section~3.2 and just
  promise that applications will come in Section~4.}
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.

>>>>

Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
%\jnote{Here it would not be hard to write the definition for general data structures, not
%specifically set-multiplicity data structures.}
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
public information $\pubaux$ that results from running $\Rep(S)$.
%\footnote{We do not give $A$ an oracle for issuing queries;
%since $A$ knows the set~$S$, such an oracle would be superfluous.
%\jnote{Interestingly,
%if we provided a query oracle in the real world and an oracle that returns the correct
%answer in the simulated world, then the definition seems to imply
%correctness also.}}
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
function~${\sf leak}$.
For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
we define the advantage
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim} \bydef
\left| \Prob{\ExpPrivSSreal{\setprim}{A}=1} -
\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|$.
Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
if for all efficient $A$ there is a simulator $\Sim$ such that
$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim}$ is small.
Intuitively, this means that the public portion
$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
\jnote{The definition
as stated does not really work well in the presence of (programmable) random oracles.}
\jnote{In the current definition there is (intentionally) no bound on the simulator's
running time.}
\todo{Mention why giving a Test oracle to A doesn't seem to help.}
\begin{figure}[tp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\setprim}{A}$}\\
$S \getsr A$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}}{A, \Sim}$}\\
$S \getsr A$\\
$\pubaux \getsr \Sim({\sf leak}(S))$ \\
return $A(\pubaux)$\\
}
}
\caption{Experiments for the ``semantic-security'' privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

\todo{A simple theorem that says if $\privaux=\emptystring$ then
  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
It's at least worth a highlighted remark, I think.  Currently it is a
remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
\todo{Since we mention what happens with $\privaux=\emptystring$, also
mention what happens with $\pubaux=\emptystring$ :)}

\heading{Relationships between the notions.}
Intuition suggests that semantic security should imply one-wayness. And, indeed, this is
the case---provided one is careful with the technical details.
For a distribution ${\cal D}$
over subsets of some universe ${\cal X}$, define
\[\tilde H_\infty({\cal D} \mid {\sf leak}) \bydef -\log \sum_{r \in R} \Pr_{S \getsr {\cal D}}[{\sf leak}(S)=r] \cdot
\max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r].\]

\fixme{Make theorem statements consistent -- get rid of $(t, \epsilon)$-style.}

@@

\heading{Privacy of ``canonical'' data structures. }
Here we prove a result that can be used to show that a large class of canonical
data structures are SS-secure, with respect to leakage of the size of the set.
\jnote{It would not be too hard to generalize this to arbitrary data structures over
arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
depends only on ${\sf leak}$.}\fixme{Action? Or remove comment?}
We first define what we mean by ``canonical.''

@@

\begin{definition}
A data structure $(\Rep, \Qry)$ is {\sf canonical} if
there exist algorithms $\Rep_1, \Rep_2$, and a function
$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
where $t$ depends only on~$n$.
\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows:
(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
(2) $K \getsr \calK$;
(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$.
%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$.
\end{itemize}
We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \hfill\dqed 
\end{definition}
\tsnote{Point out an example or two of the schemes this
  covers.  Domain-separated PRF BF, for example.  I think it covers
  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
  functions and does the hashing. (Although the following theorem does
  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
  \jnote{I say we state the general theorem in Section~3.2 and just
  promise that applications will come in Section~4.}\tsnote{Yes.}
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.
